Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2024-09-19 manuscript_latex/manuscript.tex
Correct parsing of authors.

\author[affil_1,affil_2]{Alex Zwanenburg} %% Author name

%% Author affiliation
\affiliation[affil_1]{
  organization={
    National Center for Tumor Diseases Dresden (NCT/UCC):
    German Cancer Research Center (DKFZ), Heidelberg, Germany;
    Faculty of Medicine and University Hospital Carl Gustav Carus, TUD Dresden University of Technology, Dresden, Germany;
    Helmholtz-Zentrum Dresden-Rossendorf (HZDR), Dresden, Germany
  },
  addressline={Fetscherstraße 74/PF 64},
  city={Dresden},
  postcode={01307},
  country={Germany}
}
\affiliation[affil_2]{
  organization={
    OncoRay – National Center for Radiation Research in Oncology,
    Faculty of Medicine and University Hospital Carl Gustav Carus, TUD Dresden University of Technology,
    Helmholtz-Zentrum Dresden-Rossendorf
  },
  addressline={Fetscherstraße 74/PF 41},
  city={Dresden},
  postcode={01307},
  country={Germany}
}
\author[affil_2,affil_3,affil_4]{Steffen Löck} %% Author name

%% Author affiliation
\affiliation[affil_3]{
  organization={
    Department of Radiotherapy and Radiation Oncology,
    Faculty of Medicine and University Hospital Carl Gustav Carus, TUD Dresden University of Technology
  },
  addressline={Fetscherstraße 74/PF 50},
  city={Dresden},
  postcode={01307},
  country={Germany}
}
\affiliation[affil_4]{
  organization={
   German Cancer Consortium (DKTK), Partner Site Dresden,
   and German Cancer Research Center (DKFZ)
  },
  addressline={Im Neuenheimer Feld 280},
  city={Heidelberg},
  postcode={69192},
  country={Germany}
}

@@

%%Graphical abstract
\begin{graphicalabstract}
%\includegraphics{grabs}
\end{graphicalabstract}

>>>>

%% Alex Zwanenburg
\author[affil_1,affil_2]{Alex Zwanenburg\corref{cor_note}}
\ead{alexander.zwanenburg@nct-dresden.de}
\cortext[cor_note]{corresponding author}

\affiliation[affil_1]{
  organization={
    National Center for Tumor Diseases Dresden (NCT/UCC):
    German Cancer Research Center (DKFZ), Heidelberg, Germany;
    Faculty of Medicine and University Hospital Carl Gustav Carus, TUD Dresden University of Technology, Dresden, Germany;
    Helmholtz-Zentrum Dresden-Rossendorf (HZDR), Dresden, Germany},
  addressline={Fetscherstraße 74/PF 64},
  city={Dresden},
  postcode={01307},
  country={Germany}
}
\affiliation[affil_2]{
  organization={
    OncoRay – National Center for Radiation Research in Oncology,
    Faculty of Medicine and University Hospital Carl Gustav Carus, TUD Dresden University of Technology,
    Helmholtz-Zentrum Dresden-Rossendorf},
  addressline={Fetscherstraße 74/PF 41},
  city={Dresden},
  postcode={01307},
  country={Germany}
}

%% Steffen Löck
\author[affil_2,affil_3,affil_4]{Steffen Löck}

\affiliation[affil_3]{
  organization={
    Department of Radiotherapy and Radiation Oncology,
    Faculty of Medicine and University Hospital Carl Gustav Carus, TUD Dresden University of Technology},
  addressline={Fetscherstraße 74/PF 50},
  city={Dresden},
  postcode={01307},
  country={Germany}
}
\affiliation[affil_4]{
  organization={
   German Cancer Consortium (DKTK), Partner Site Dresden,
   and German Cancer Research Center (DKFZ)},
  addressline={Im Neuenheimer Feld 280},
  city={Heidelberg},
  postcode={69192},
  country={Germany}
}

@@

%%Graphical abstract
% \begin{graphicalabstract}
% \includegraphics{grabs}
% \end{graphicalabstract}
